Expert pianists make specific exaggerations for teaching

### 2023-01-07 paper/manuscript.Rmd
update citation style for docx file
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>
remove one space
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

#output: papaja::apa6_word
output:
  papaja::apa6_pdf:
    latex_engine: xelatex
---

@@

A paired-sample *t*-test showed that participants played more slowly in the teaching condition [*M* = `r sprintf('%.2f', ioi_art_all[Condition == "teaching"]$Mean)`, *SD* = `r sprintf('%.3f', ioi_art_all[Condition == "teaching"]$SD)`] than in the performing condition [*M* = `r sprintf('%.2f', ioi_art_all[Condition == "performing"]$Mean)`, *SD* = `r sprintf('%.3f', ioi_art_all[Condition == "performing"]$SD)`] while playing the piece with the notated articulation (*t*(`r ioi_art_ttest$parameter`) = `r sprintf('%.2f', abs(ioi_art_ttest$statistic))`
, *p* `r if(ioi_art_ttest$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', ioi_art_ttest$p.value))}`, Cohen's *d* = `r round(abs(coheneff_art$effsize), 3)`, two-tailed, *Fig \ref{fig:ioi-2}*). A Wilcoxon Signed-rank test also confirmed that there was a significant difference between the two conditions (*p* `r if(ioi_art_wilcoxon$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', ioi_art_wilcoxon$p.value))}`, *r* = `r round(wilcoxeff_art$effsize, 2)`, two-tailed).

>>>>

# documentclass     : "apa6" # for word
# classoption       : "man" # for word
# output: papaja::apa6_word # for word
output: 
  papaja::apa6_pdf:
    latex_engine: xelatex # for pdf
---

@@

A paired-sample *t*-test showed that participants played more slowly in the teaching condition [*M* = `r sprintf('%.2f', ioi_art_all[Condition == "teaching"]$Mean)`, *SD* = `r sprintf('%.3f', ioi_art_all[Condition == "teaching"]$SD)`] than in the performing condition [*M* = `r sprintf('%.2f', ioi_art_all[Condition == "performing"]$Mean)`, *SD* = `r sprintf('%.3f', ioi_art_all[Condition == "performing"]$SD)`] while playing the piece with the notated articulation (*t*(`r ioi_art_ttest$parameter`) = `r sprintf('%.2f', abs(ioi_art_ttest$statistic))`, *p* `r if(ioi_art_ttest$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', ioi_art_ttest$p.value))}`, Cohen's *d* = `r round(abs(coheneff_art$effsize), 3)`, two-tailed, *Fig \ref{fig:ioi-2}*). A Wilcoxon Signed-rank test also confirmed that there was a significant difference between the two conditions (*p* `r if(ioi_art_wilcoxon$p.value < 0.001){"< 0.001"} else {paste("= ", sprintf('%.3f', ioi_art_wilcoxon$p.value))}`, *r* = `r round(wilcoxeff_art$effsize, 2)`, two-tailed).

### 2023-01-07 paper/manuscript.tex
remove one space
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

A paired-sample \emph{t}-test showed that participants played more slowly in the teaching condition {[}\emph{M} = 0.97, \emph{SD} = 0.049{]} than in the performing condition {[}\emph{M} = 0.95, \emph{SD} = 0.040{]} while playing the piece with the notated articulation (\emph{t}(19) = 2.47
, \emph{p} = 0.023, Cohen's \emph{d} = 0.55, two-tailed, \emph{Fig \ref{fig:ioi-2}}). A Wilcoxon Signed-rank test also confirmed that there was a significant difference between the two conditions (\emph{p} = 0.033, \emph{r} = 0.48, two-tailed).

>>>>

A paired-sample \emph{t}-test showed that participants played more slowly in the teaching condition {[}\emph{M} = 0.97, \emph{SD} = 0.049{]} than in the performing condition {[}\emph{M} = 0.95, \emph{SD} = 0.040{]} while playing the piece with the notated articulation (\emph{t}(19) = 2.47, \emph{p} = 0.023, Cohen's \emph{d} = 0.55, two-tailed, \emph{Fig \ref{fig:ioi-2}}). A Wilcoxon Signed-rank test also confirmed that there was a significant difference between the two conditions (\emph{p} = 0.033, \emph{r} = 0.48, two-tailed).
